Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-09 ms.tex
updated PCA with non-standardized version.

\subsection{PCA Analysis}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using the average light curve (Top Right).
(Bottom) The residuals show significant deviations at phases of -0.5 and 0.05.
}\label{fig:riverPlots}
\end{centering}
\end{figure*}

As another way of analyzing the light curve data, we apply Principal Component Analysis (PCA) to this two dimensional grid.
We start by rescaling the two dimensional grid to have zero mean and a variance of 1.0 along the Transit Number axis, while saving the transformation to return to the original flux units.
This first rescaling step will remove the constants from the transit light curve (such as the planet candidate's transit curve).
Next, we perform PCA on the two dimensional grid to identify eigenvectors as a function of orbital phase and then the principal components as a function of transit number.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.45\textwidth]{images/kepler/amplitude_series.pdf}
\caption{Principal component eigenvectors (Left) and amplitude time series (Right).}\label{fig:PCAamp}
\end{centering}
\end{figure*}

@@

>>>>

\subsection{Average Light Curve Analysis}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.3\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.3\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.3\textwidth]{images/kepler/residual_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
(Right) The residuals show significant deviations at phases of -0.5 and 0.05.
}\label{fig:riverPlots}
\end{centering}
\end{figure*}

\subsection{Principal Component Analysis}

As another way of analyzing the light curve data, we apply Principal Component Analysis (PCA) to this two dimensional grid.
Here, we are assuming that the grid of orbital phases (spaced by 15 minutes) contains random correlated variables with different realizations along the transit number axis.
The first principal component eigenvector is the linear combination of these random variables that maximizes the variance in the data.
The second principal component eigenvector is the linear combination of these random variables with the next-highest variance while being orthogonal to the first principal component.
This continues up to some finite number of principal components, with the hope that we can use just a few orthogonal light curves to adequately describe the data \citep[e.g.][]{jolliffe2002pca}.
We use the Python package \texttt{scikit-learn} \citep{pedregosa2011scikit-learn} to calculate the principal components and eigenvectors.

It is customary with PCA to scale the variables to have zero mean and a variance of 1.0 (ie. along the Transit Number axis) before performing PCA.
However, we elect to keep the original variables without scaling each column in this 2D grid by its standard deviation, since that would magnify the contribution of photon noise in out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.1 to $\sim$ 0.1).
Next, we perform PCA on the two dimensional grid to identify eigenvectors as a function of orbital phase and then the principal components as a function of transit number.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
\caption{Principal component eigenvectors (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scatterg.
The first two principal components (Right) do not isolate any separate populations of transits.
As expected, the quiescent periods show up as low principal component contributions from both of the two eigenvectors (ie. a flatter light curve)}.
\end{centering}
\end{figure*}

@@

\facility{Subaru}

\software{astropy \citep{astropy2013}, 
	\texttt{scikit-learn} \citep{pedregosa2011scikit-learn},
	\texttt{iraf},
	\texttt{specmatch} tool \citep{yee2017specMatch} 
          %\texttt{emcee} \citep{foreman-mackey2013emcee}, 
          }
